Discrepancy, Coresets, and Sketches in Machine Learning

### 2019-01-30 komlos.tex
minor stuff

The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors\footnote{We Assume that $\|x\|,\|q\| \leq 1$ for ease of presentation. As above our results extend to generic bounds on the radius of $q$} $q$. By controlling all powers of $\ip{q,x}$ we control any sum of these powers. It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$ or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$. \todo{Can we say the same for $1/(1 + \exp(\ip{q,x}))$. It might be more interesting than the logistic loss cos it's not convex...}

>>>>

The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors\footnote{We Assume that $\|x\|,\|q\| \leq 1$ for ease of presentation. As above our results extend to generic bounds on the radius of $q$} $q$. By controlling all powers of $\ip{q,x}$ we control any sum of these powers. It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$, sigmoid activation $\sigma(q,x)=1/(1 + \exp(\ip{q,x}))$, or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
